### 2019-11-19 paper-body.tex
Fixed: Warnings relating to floating graphs. TODO: Better sizes for error graphs
Fixed: Algorithms section no longer causes error with texcount
Fixed: Typos

\chapter{Background and Related Work}
\section{Real-time Physics Engines}
%We must first understand how real-time physics engines work
%"World" is called a scene, "Bodies" are things being simulated
%Descrete simulation steps, each step simulates a period of time

@@

		\State $\textit{island := \{\}}$
		\State $\textit{isIsland := }\Call{IslandQuery}{\textit{object, island}}$
		\LeftComment{IslandQuery() returns true if object is part of an island and a list of objects in the island}
		\If {$\textit{isIsland} = \textit{true}$}:
		\State \Call{SendGroup}{$\textit{island}$}
		\EndIf
		\State $\textit{checked := checked + island}$
		\EndFor
		%		\State $\textit{visited := \{\}}$	\Comment{Track visited to prevent infinite recursion}
		%		\State \Call{SendWithOverlaps}{$\textit{thisObject, visited}$}
		\EndProcedure
		\State
		\Function{IslandQuery}{$\textit{object, visited}$}
		\State $\textit{visited := visited + object}$
		\If {$\textit{object.overlapsHostRegion = true}$}
		\State return $\textit{false}$
		\EndIf
		%\If {$\textit{object.boundaryCollisionCount = 0}$}
		%\State return $\textit{false}$
		%\EndIf
		\State
		\LeftComment{Get objects whose auras overlap this object's aura} %using a $\mathcal{O}(n)$ scene query
		\State $\textit{overlaps :=}$ \Call{GetMutalAuraOverlaps}{$\textit{object}$}
		\State
		\LeftComment{If all objects with overlapping auras are islands, then this object is an island}
		\State $\textit{isIsland := true}$
		\ForAll{{$\textit{object} \in \textit{overlaps}$}} :
		\If {$\textit{object} \not \in \textit{visited}$}:
		\State $\textit{isIsland \&= }\Call{IslandQuery}{\textit{object,visited}$}
		\EndIf
		\EndFor
		\State return $\textit{isIsland}$
		\EndFunction
		%		
		%		\Procedure{SendWithOverlaps}{$\textit{object, visited}$}
		%		\State $\textit{overlaps :=}$ \Call{GetOverlaps}{$\textit{object}$} \Comment{$\mathcal{O}(n)$ scene query}
		%		\ForAll{{$\textit{object} \in \textit{overlaps}$}} :
		%		\If {$\textit{object} \not \in \textit{visited}$}:
		%		\State $\textit{visited := visited + object}$
		%		\State \Call{SendWithOverlaps}{$\textit{object, visited}$}
		%		\EndIf
		%		\EndFor
		%		
		%		\State\Call{Send}{object}
		%		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

To understand how late collisions lead to unstable collision response, we must first understand how in real-time collision detection works. In real-time physics engines, objects move in descrete steps, as a result of this, when two objects collide, they overlap each other i.e. penetrate. The collision is resolved by calculating the forces resulting from the collision and moving the objects so they no longer overlap (in PhysX if penetration is high, the latter may be done over several physics time-steps). If the penetration is high, such as in the case of a late collision response or if two objects are moving at high speed towards one another, the collision response can no longer guarantee stable results.

@@

As relative speed increases, expected penetration increases and the erroneous penetration distance for the same aura error (aura too small or aura receive message delayed) also increases. Using Penetration time gives us a uniform error regardless of relative speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and relative speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in descrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous.

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
	\label{fig_CollisionsPenVsSpeed}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
\caption{The mean and max of collision errors with varying relative speed}
\label{fig_MeanMaxErrorVsSpeed}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{RatiosVsSpeed}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
\label{fig_RatiosVsSpeed}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsLatency}
\caption{Penetration time of objects with varying latency. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. The number and magnitude of errors increases as latency increases beyond the tolerance.}
\label{fig_CollisionsPenVsLatency}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsLatency}
\caption{The mean and max of collision errors with varying latency}
\label{fig_MeanMaxErrorVsLatency}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{RatiosVsLatency}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying latency}
\label{fig_RatiosVsLatency}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsFrameTime}
\caption{Penetration time of objects with varying frame-time. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as target frame-time increases beyond the tolerance.}
\label{fig_CollisionsPenVsFrameTime}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsFrameTime}
\caption{The mean and max of collision errors with varying frame-time}
\label{fig_MeanMaxErrorVsFrameTime}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{RatiosVsFrameTime}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying frame-time}
\label{fig_RatiosVsFrameTime}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsLoss}
\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
\label{fig_CollisionsPenVsLoss}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsLoss}
\caption{The mean and max of collision errors with varying packet loss. As packet-loss increases from $10\%$ to $20\%$ the magnitude of errors sharply increases until above $60\%$ where all collisions are missed so there is no error.}
\label{fig_MeanMaxErrorVsLoss}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{RatiosVsLoss}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss. As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
\label{fig_RatiosVsLoss}
\end{figure}

>>>>

\chapter{Background and Related Work}
\section{Real-time Physics Engines}
%We must first understand how real-time physics engines work
%"World" is called a scene, "Bodies" are things being simulated
%discrete simulation steps, each step simulates a period of time

@@

		\State $\textit{island := \{\}}$
		\State $\textit{isIsland := }\Call{IslandQuery}{\textit{object, island}}$
		\LeftComment{IslandQuery() returns true if object is part of an island and a list of objects in the island}
		\If {$\textit{isIsland} = \textit{true}$}:
		\State \Call{SendGroup}{$\textit{island}$}
		\EndIf
		\State $\textit{checked := checked + island}$
		\EndFor
		%		\State $\textit{visited := \{\}}$	\Comment{Track visited to prevent infinite recursion}
		%		\State \Call{SendWithOverlaps}{$\textit{thisObject, visited}$}
		\EndProcedure
		\State
		\Function{IslandQuery}{$\textit{object, visited}$}
		\State $\textit{visited := visited + object}$
		\If {$\textit{object.overlapsHostRegion = true}$}
		\State return $\textit{false}$
		\EndIf
		%\If {$\textit{object.boundaryCollisionCount = 0}$}
		%\State return $\textit{false}$
		%\EndIf
		\State
		\LeftComment{Get objects whose auras overlap this object's aura} %using a $\mathcal{O}(n)$ scene query
		\State $\textit{overlaps :=}$ \Call{GetMutalAuraOverlaps}{$\textit{object}$}
		\State
		\LeftComment{If all objects with overlapping auras are islands, then this object is an island}
		\State $\textit{isIsland := true}$
		\ForAll{{$\textit{object} \in \textit{overlaps}$}} :
		\If {$\textit{object} \not \in \textit{visited}$}:
		\State $\textit{isIsland \&= }$ \Call{IslandQuery}{$\textit{object,visited}$}
		\EndIf
		\EndFor
		\State return $\textit{isIsland}$
		\EndFunction
		%		
		%		\Procedure{SendWithOverlaps}{$\textit{object, visited}$}
		%		\State $\textit{overlaps :=}$ \Call{GetOverlaps}{$\textit{object}$} \Comment{$\mathcal{O}(n)$ scene query}
		%		\ForAll{{$\textit{object} \in \textit{overlaps}$}} :
		%		\If {$\textit{object} \not \in \textit{visited}$}:
		%		\State $\textit{visited := visited + object}$
		%		\State \Call{SendWithOverlaps}{$\textit{object, visited}$}
		%		\EndIf
		%		\EndFor
		%		
		%		\State\Call{Send}{object}
		%		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

To understand how late collisions lead to unstable collision response, we must first understand how in real-time collision detection works. In real-time physics engines, objects move in discrete steps, as a result of this, when two objects collide, they overlap each other i.e. penetrate. The collision is resolved by calculating the forces resulting from the collision and moving the objects so they no longer overlap (in PhysX if penetration is high, the latter may be done over several physics time-steps). If the penetration is high, such as in the case of a late collision response or if two objects are moving at high speed towards one another, the collision response can no longer guarantee stable results.

@@

As relative speed increases, expected penetration increases and the erroneous penetration distance for the same aura error (aura too small or aura receive message delayed) also increases. Using Penetration time gives us a uniform error regardless of relative speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and relative speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in discrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
	\label{fig_CollisionsPenVsSpeed}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
\caption{The mean and max of collision errors with varying relative speed}
\label{fig_MeanMaxErrorVsSpeed}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{RatiosVsSpeed}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
\label{fig_RatiosVsSpeed}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsLatency}
\caption{Penetration time of objects with varying latency. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. The number and magnitude of errors increases as latency increases beyond the tolerance.}
\label{fig_CollisionsPenVsLatency}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsLatency}
\caption{The mean and max of collision errors with varying latency}
\label{fig_MeanMaxErrorVsLatency}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{RatiosVsLatency}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying latency}
\label{fig_RatiosVsLatency}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsFrameTime}
\caption{Penetration time of objects with varying frame-time. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as target frame-time increases beyond the tolerance.}
\label{fig_CollisionsPenVsFrameTime}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsFrameTime}
\caption{The mean and max of collision errors with varying frame-time}
\label{fig_MeanMaxErrorVsFrameTime}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{RatiosVsFrameTime}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying frame-time}
\label{fig_RatiosVsFrameTime}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{CollisionsPenVsLoss}
\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
\label{fig_CollisionsPenVsLoss}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{MeanMaxErrorVsLoss}
\caption{The mean and max of collision errors with varying packet loss. As packet-loss increases from $10\%$ to $20\%$ the magnitude of errors sharply increases until above $60\%$ where all collisions are missed so there is no error.}
\label{fig_MeanMaxErrorVsLoss}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{RatiosVsLoss}
\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss. As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
\label{fig_RatiosVsLoss}
\end{figure}
